### 2014-02-19 brains-protocol.tex
More info on the fact-checks
Update remarks after today's conversation on current issues

\begin{itemize}
    \item \textbf{Age of Acquisition}: the average age at which words are learned, obtained from~\citet{kuperman12},
    \item The average \textbf{Number of Phonemes} for all pronunciations of a word, obtained from the Carnegie Mellon University Pronouncing Dictionary~\citep{Weide98},\footnote{The CMU Pronouncing Dictionary is included in the NTLK package~\citep{Bird09}, the natural language processing toolkit we used for the analysis.}
    \item The average \textbf{Number of Syllables} for all pronunciations of a word, also obtained from the CMU Pronouncing Dictionary.
    \item \rk{Why exactly don't we include word frequencies as a measure? The alleged self-correlation loop doesn't determine at which end of a substitution a given high-frequency word would be, so it doesn't really force correlation}
\end{itemize}

@@

While the original WN network is a weighted, undirected network, the FA network is a directed network where weights have a different meaning.
Both semantic networks describe synonymy relationships corresponding to qualitatively distinct forms of association: either from a linguistic viewpoint (WN) or from the perspective of actual information retrieval by humans (FA).
In  order to work in a unified framework, we shall consider links as an information on the existence of some sort of association between two words and transform both networks into undirected, unweighed networks.
\rk{Check that's the case in the analysis}
\rk{In fact, the graphs are much less interesting for undirected unweighed FA.}

@@

\begin{itemize}
    \item \textbf{Distance} between two words, a classical dyadic network measure corresponding to the shortest path length between two nodes.
    This measure may be used as a proxy of the remoteness between two given words, which is likely to influence the likelihood of a word being a relevant substitution candidate for another word.
    \item \textbf{Centrality} $k$, measured by the number of neighbours of a given node, which can be interpreted as a proxy for the polysemy of words.
    \TB{For the directed network FA we also define the incoming centrality $k'$ (number of neighbours pointing \emph{to} that node)}.
    \rk{Remove that, since we restrict ourselves to undirected networks}
    Note that in the present case, there is a quasi-perfect correlation between node degree and node \emph{PageRank}~\citep{Page99}, which had already been used in~\citet{Griffiths07} and may be interpreted as a generalized and recursive measure of word polysemy: central nodes in the PageRank sense are those which are linked to many nodes themselves linked to many nodes, and so on recursively.
    \item \textbf{Clustering coefficient} $c$, which measures the extent to which a node belongs to a local aggregate of tightly connected nodes, and defined as the ratio between the number of actual v. possible edges between a node's neighbours \cite{watt-coll}.
    In the WN network, a word is likely to have a higher clustering coefficient whenever the synsets to which it belongs are themselves semantically linked.
    This measure had been used by \citet{Chan10}.
\end{itemize}

@@

We introduce a null hypothesis $\mathcal{H}_0$ to compare the actual variation of a word's feature to its expected variation, assuming the arrival word $\warrival_{\mathcal{H}_0}$ had been chosen randomly from the pool of free association words.
\rk{Check that's true in the code}
The corresponding average quantity over all start words may be written:
\footnote{Note that $\warrival_{\mathcal{H}_0}$ is in fact constant in this averaging, since by definition it does not depend on $\wstart$.}
$$\left< \Delta(\wstart,\warrival_{\mathcal{H}_0}) \right>_f = \left< \mathfrak{F}({\warrival_{\mathcal{H}_0}}) - \mathfrak{F}(\wstart) \right>_{\left\lbrace (\wstart,\warrival_{\mathcal{H}_0}) | \mathfrak{F}(\wstart) = f \right\rbrace}$$

>>>>

\begin{itemize}
    \item \rk{Add word frequency as a feature, and maybe link it to Kolmogorov's 5/3 law in turbulences}
    \item \textbf{Age of Acquisition}: the average age at which words are learned, obtained from~\citet{kuperman12},
    \item The average \textbf{Number of Phonemes} for all pronunciations of a word, obtained from the Carnegie Mellon University Pronouncing Dictionary~\citep{Weide98},\footnote{The CMU Pronouncing Dictionary is included in the NTLK package~\citep{Bird09}, the natural language processing toolkit we used for the analysis.}
    \item The average \textbf{Number of Syllables} for all pronunciations of a word, also obtained from the CMU Pronouncing Dictionary.
\end{itemize}

@@

While the original WN network is a weighted, undirected network, the FA network is a directed network where weights have a different meaning.
Both semantic networks describe synonymy relationships corresponding to qualitatively distinct forms of association: either from a linguistic viewpoint (WN) or from the perspective of actual information retrieval by humans (FA).
In  order to work in a unified framework, we shall consider links as an information on the existence of some sort of association between two words and transform both networks into undirected, unweighed networks.
\rk{Roll back to directed FA, and explain that it's a link between in-vivo spontaneous substitution and in-vitro forced substitution.
We could even add a more precise analysis using FA data directly (instead of features on the FA network), or keep that for the processual model.}

@@

\begin{itemize}
    \item \textbf{Distance} between two words, a classical dyadic network measure corresponding to the shortest path length between two nodes.
    This measure may be used as a proxy of the remoteness between two given words, which is likely to influence the likelihood of a word being a relevant substitution candidate for another word.
    \item \textbf{Centrality} $k$, measured by the number of neighbours of a given node, which can be interpreted as a proxy for the polysemy of words.
    \TB{For the directed network FA we also define the incoming centrality $k'$ (number of neighbours pointing \emph{to} that node)}.
    \rk{Rephrase once we rolled back FA to directed}
    Note that in the present case, there is a quasi-perfect correlation between node degree and node \emph{PageRank}~\citep{Page99}, which had already been used in~\citet{Griffiths07} and may be interpreted as a generalized and recursive measure of word polysemy: central nodes in the PageRank sense are those which are linked to many nodes themselves linked to many nodes, and so on recursively.
    \item \textbf{Clustering coefficient} $c$, which measures the extent to which a node belongs to a local aggregate of tightly connected nodes, and defined as the ratio between the number of actual v. possible edges between a node's neighbours \cite{watt-coll}.
    In the WN network, a word is likely to have a higher clustering coefficient whenever the synsets to which it belongs are themselves semantically linked.
    This measure had been used by \citet{Chan10}.
\end{itemize}

@@

We introduce a null hypothesis $\mathcal{H}_0$ to compare the actual variation of a word's feature to its expected variation, assuming the arrival word $\warrival_{\mathcal{H}_0}$ had been chosen randomly from the pool of free association words.
The corresponding average quantity over all start words may be written:
\footnote{Note that $\warrival_{\mathcal{H}_0}$ is in fact constant in this averaging, since by definition it does not depend on $\wstart$.}
$$\left< \Delta(\wstart,\warrival_{\mathcal{H}_0}) \right>_f = \left< \mathfrak{F}({\warrival_{\mathcal{H}_0}}) - \mathfrak{F}(\wstart) \right>_{\left\lbrace (\wstart,\warrival_{\mathcal{H}_0}) | \mathfrak{F}(\wstart) = f \right\rbrace}$$
